Modelling the emergence of whisker barrels

### 2020-07-09 paper/briefpaper/brief.tex
Re-word the statement about dot(a_i) prop. dot(c_i)

% Brief report style paper

@@

\cite{karbowski_model_2004} developed a reaction-diffusion style model of how
extrinsic signalling gradients can constrain the emergence of distinct fields
from intrinsic cortical dynamics. Their model defines how the \cmnt{fraction
  of occupied synapses} $c_i(x,t)$ and \cmnt{the density of} axon branches
$a_i(x,t)$ interact at time $t$, along a 1D anterior-posterior axis $x$, for
$N$ thalamocortical projections indexed by $i$. The model was derived from the
assumption that the rates at which $a_i$ and $c_i$ grow are reciprocally
coupled. Extending the original 1D model to simulate arealisation on a 2D
cortical sheet, we use $a_i(\mb{x},t)$ and $c_i(\mb{x},t)$, and model
synaptogenesis as
%
\begin{equation} \label{eq:dc}
\frac{\partial c_i}{\partial t} =-\alpha c_i +\beta  \left(1 - \sum_{j=1}^{N} c_{j}\right)[a_i]^k.
\end{equation}
%
Accordingly, where the total \cmnt{fraction} of synaptic connections sums to one,
connections decay at rate $\alpha$. Otherwise, \cmnt{$c_i(\mb{x},t)$} increases
non-linearly ($k>1$) with the density of axon branching. Axon branching is
modelled as
%
\begin{equation} \label{eq:da}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x}) \MPtwo{+ \chi_i}\right) - \frac{\partial c_i}{\partial t}.
\end{equation}
%
The first term on the right describes the divergence (indicated by
$\nabla\vcdot$) of the quantity in parentheses, which is referred to as the
`flux' of axonal branching. The flux represents diffusion across the cortical
sheet, at rate $D$, and the influence of $M$ molecular signalling fields,
$\rho(\mb{x})$. The influence of a given field (indexed by $j$) on a given
thalamic projection (indexed by $i$), is determined by $\gamma_{i,j}$, which
may be positive or negative in order that axons may branch in the direction of
either higher or lower concentrations. Note that computing the divergence in
simulation requires cells on the cortical sheet to communicate with immedately
adjacent cells only (see \emph{Materials \& Methods}). Here $\chi_i=0$ is a
placeholder. The second term on the right represents the coupling between axon
branching and synaptogenesis \cmnt{and implies an assumption of spatially
  homogeneous synaptic density which makes it possible to relate the quantity
  $c_i$ to connection density}.

>>>>

% (This started life as a...) Brief report style paper

@@

\cite{karbowski_model_2004} developed a reaction-diffusion style model of how
extrinsic signalling gradients can constrain the emergence of distinct fields
from intrinsic cortical dynamics. Their model defines how the \cmnt{fraction
  of occupied synapses} $c_i(x,t)$ and \cmnt{the density of} axon branches
$a_i(x,t)$ interact at time $t$, along a 1D anterior-posterior axis $x$, for
$N$ thalamocortical projections indexed by $i$. The model was derived from the
assumption that the rates at which $a_i$ and $c_i$ grow are reciprocally
coupled. Extending the original 1D model to simulate arealisation on a 2D
cortical sheet, we use $a_i(\mb{x},t)$ and $c_i(\mb{x},t)$, and model
synaptogenesis as
%
\begin{equation} \label{eq:dc}
\frac{\partial c_i}{\partial t} =-\alpha c_i +\beta  \left(1 - \sum_{j=1}^{N} c_{j}\right)[a_i]^k.
\end{equation}
%
Accordingly, where the total \cmnt{fraction} of synaptic connections sums to one,
connections decay at rate $\alpha$. Otherwise, \cmnt{$c_i(\mb{x},t)$} increases
non-linearly ($k>1$) with the density of axon branching. Axon branching is
modelled as
%
\begin{equation} \label{eq:da}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x}) \MPtwo{+ \chi_i}\right) - \frac{\partial c_i}{\partial t}.
\end{equation}
%
The first term on the right describes the divergence (indicated by
$\nabla\vcdot$) of the quantity in parentheses, which is referred to as the
`flux' of axonal branching. The flux represents diffusion across the cortical
sheet, at rate $D$, and the influence of $M$ molecular signalling fields,
$\rho(\mb{x})$. The influence of a given field (indexed by $j$) on a given
thalamic projection (indexed by $i$), is determined by $\gamma_{i,j}$, which
may be positive or negative in order that axons may branch in the direction of
either higher or lower concentrations. Note that computing the divergence in
simulation requires cells on the cortical sheet to communicate with immedately
adjacent cells only (see \emph{Materials \& Methods}). Here $\chi_i=0$ is a
placeholder. The second term on the right represents the coupling between axon
branching and synaptogenesis \cmnt{and implies the assumption that the spatial
  distribution of synaptic density across the cortical sheet is broadly
  homogeneous. This makes it possible to relate the quantity $c_i$ to
  connection density}.
